---
title: "Module 1"
subtitle: "{{< var md-01.title >}}"
editor: source
params:
    module: 1
execute: 
  echo: false
  warning: false
bibliography: references.bib
editor_options: 
  chunk_output_type: console
---

This first week will be used to get you set up for the course. 

## Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-01-rbtl-fs24-learning-objectives.csv")) |> 
  dplyr::filter(module == params$module) |>
  dplyr::pull(learning_objectives)

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa display >}} Slides

[View slides in full screen](../slides/lec-01-welcome.html) | [Download slides as PDF](https://github.com/rbtl-fs24/website/raw/main/slides/lec-01-welcome.pdf)

```{=html}
<iframe class="slide-deck" src="../slides/lec-01-welcome.html" height="420" width="747" style="border: 1px solid #123233;"></iframe>
```


## {{< fa book >}} Readings

- Read the [Course Overview](../overview.html).

## {{< fa code >}} Assignments

Please complete the following assignments by Wednesday, 28th February 2024. They are a pre-requisite for active participation in the second module.

-   [Assignment 1](../assignments/md-01/am-01-1-github.qmd): In class: Get an account for GitHub
-   [Assignment 2](../assignments/md-01/am-01-2-posit.qmd): In class: Working with R, RStudio on Posit Cloud
-   [Assignment 3](../assignments/md-01/am-01-3-github.qmd): Homework: Interaction with GitHub
-   Assignment 4: Create your ORCID iD at: <https://orcid.org/register> ([Learn more about ORCID and why you should get one](https://the-turing-way.netlify.app/communication/citable/citable-orcid.html?highlight=orcid))
-   Assignment 5: Complete the pre-course survey (this is also your assignment submission completed): <https://forms.gle/jcKFqiB2DHmSSbck6>

Thank you for working through these assignments. 