---
title: "Module 1"
subtitle: "Welcome & get ready for the course"
editor: source
params:
    week: 1
execute: 
  echo: false
  warning: false
bibliography: references.bib
editor_options: 
  chunk_output_type: console
---

This first week will be used to get you set up for the course. 

## Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-02-ds4owd-001-learning-objectives.csv")) |> 
  dplyr::filter(week == params$week) |>
  dplyr::pull(learning_objectives)

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```


## {{< fa display >}} Slides

[View slides in full screen](../slides/lec-01-welcome.html) | [Download slides as PDF](https://github.com/ds4owd-001/website/raw/main/slides/lec-01-welcome.pdf)

```{=html}
<iframe class="slide-deck" src="../slides/lec-01-welcome.html" height="420" width="747" style="border: 1px solid #123233;"></iframe>
```


## {{< fa book >}} Readings

- Read the [Course Overview](../overview.html).

## {{< fa code >}} Assignments

Please complete the following assignments by Monday, 6th November 2023. They are a pre-requisite for the second module.

-   [Assignment 1](../assignments/md-01/am-01-1-posit.qmd): In class: Working with R, RStudio on Posit Cloud
-   [Assignment 2](../assignments/md-01/am-01-2-element.qmd): Homework: Communication in a chat
-   [Assignment 3](../assignments/md-01/am-01-3-github.qmd): Homework: Interaction with GitHub

Thank you for working through these assignments. 