---
title: "Module 08"
subtitle: "Waste Research"
editor: source
params:
    module: 8
execute: 
  echo: false
  warning: false
---

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-01-rbtl-fs24-learning-objectives.csv")) |> 
  dplyr::filter(module == params$module) |>
  dplyr::pull(learning_objectives)

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa display >}} Slides

[View slides in full screen](../slides/lec-08-waste-research.html) | [Download slides as PDF](https://github.com/rbtl-fs24/website/raw/main/slides/lec-08-waste-research.pdf)

```{=html}
<iframe class="slide-deck" src="../slides/lec-08-waste-research.html" height="420" width="747" style="border: 1px solid #123233;"></iframe>
```

## {{< fa book >}} Readings

1. [Kasinja, C., & Tilley, E. (2018). Formalization of informal waste pickers’ cooperatives in Blantyre, Malawi: A feasibility assessment. Sustainability, 10(4), 1149.](https://drive.google.com/file/d/1EBAUWsYtcR4FDcxekdMNNif5WTAaNfix/view?usp=sharing)
2. [Ndau, H., & Tilley, E. (2018). Willingness to pay for improved household solid waste collection in Blantyre, Malawi. Economies, 6(4), 54.](https://drive.google.com/file/d/1EIKQY9-nzUsCy-P2ATbH0Cuqq741qLnj/view?usp=sharing)
3. [Roxburgh, H., Magombo, C., Kaliwo, T., Tilley, E. A., Hampshire, K., Oliver, D. M., & Quilliam, R. S. (2022). Blood flows: mapping journeys of menstrual waste in Blantyre, Malawi. Cities & Health, 6(4), 738-751.](https://drive.google.com/file/d/1EQn5_tA9N5MzDTmQJKpT-3syBRC-B4Yn/view?usp=sharing)
4. [Tilley, E., Chilunga, H., Kwangulero, J., Schöbitz, L., Vijay, S., Heilgendorff, H., & Kalina, M. (2023). “It is unbearable to breathe here”: air quality, open incineration, and misinformation in Blantyre, Malawi. Frontiers in Public Health, 11, 1242726.](https://drive.google.com/file/d/1EGT9NScqVPmZ1M5u4mRLswx3BFoMNxpV/view?usp=sharing)
5. [Yesaya, M., Mpanang'ombe, W., & Tilley, E. (2021). The cost of plastics in compost. Frontiers in Sustainability, 2, 753413.](https://drive.google.com/file/d/1EDNXOWlJYOuh0LZg_G0nqX40yRQCtMQn/view?usp=sharing)

## {{< fa code >}} Assignments

Please complete the following assignment by Wednesday, 24th April 2024. 

-   [Assignment 1](../assignments/md-08/am-08-2-presentation.qmd): This assignment will be communicated in class

