---
title: "Module 09"
subtitle: "Research Design"
editor: source
params:
    module: 9
execute: 
  echo: false
  warning: false
---

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-01-rbtl-fs24-learning-objectives.csv")) |> 
  dplyr::filter(module == params$module) |>
  dplyr::pull(learning_objectives)

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```


## {{< fa display >}} Slides

- You will present your homework in this module. There are no additional slides.

## {{< fa code >}} Assignments
Please complete the following assignments by Wednesday, 1 May 2024.

1. Read [Fandino, W. (2019). Formulating a good research question: Pearls and pitfalls. Indian Journal of Anaesthesia, 63(8), 611-616](https://drive.google.com/file/d/1PKZDMm23e5n_22T9zHyRbtcQI2_7_-7G/view).
2. Formulate your own research question according to the FINER and PICOT methods. Be prepared to discuss.

