---
title: "Module 6"
subtitle: "{{< var md-06.title >}}"
editor: source
params:
    module: 6
execute: 
  echo: false
  warning: false
---

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-01-rbtl-fs24-learning-objectives.csv")) |> 
  dplyr::filter(module == params$module) |>
  dplyr::pull(learning_objectives)

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa display >}} Slides

[View slides in full screen](../slides/lec-06-vectors.html) | [Download slides as PDF](https://github.com/rbtl-fs24/website/raw/main/slides/lec-06-vectors.pdf)

```{=html}
<iframe class="slide-deck" src="../slides/lec-06-vectors.html" height="420" width="747" style="border: 1px solid #123233;"></iframe>
```

## {{< fa book >}} Readings

1. Read [R for Data Science - Section 5 - Data tidying](https://r4ds.hadley.nz/data-tidy)
1. Read [R for Data Science - Section 7 - Data import](https://r4ds.hadley.nz/data-import)  
2. Read [R for Data Science - Section 10 - Exploratory data analysis](https://r4ds.hadley.nz/eda)  

## {{< fa code >}} Assignments

Please complete the following assignment by Wednesday, 10th April 2024. 

-   [Assignment 1](../assignments/md-06/am-06-1-reading.qmd): Good enough practices in scientific computing
-   [Assignment 2](../assignments/md-06/am-06-2-pivoting.qmd): Pivot your data 
-   [Assignment 3](../assignments/md-06/am-06-3-project.qmd): Setup your capstone project repository
