---
title: "Module 2"
subtitle: "{{< var md-02.title >}}"
editor: source
params:
    module: 2
execute: 
  echo: false
  warning: false
bibliography: ../ds4owd-001.bib
---

Are you ready for some data visualisations? This week is all about exploring data with `ggplot2` R package. We will also learn about the data science lifecycle. 

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-01-rbtl-fs24-learning-objectives.csv")) |> 
  dplyr::filter(module == params$module) |>
  dplyr::pull(learning_objectives)

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa display >}} Slides

- In preparation

## {{< fa book >}} Readings

1. Read [R for Data Science - Whole game](https://r4ds.hadley.nz/whole-game)
2. Read [R for Data Science - Section 3 - Workflow basics](https://r4ds.hadley.nz/workflow-basics) 
3. Read [R for Data Science - Section 2 - Data visualization](https://r4ds.hadley.nz/data-visualize)

## {{< fa code >}} Assignments

- In preparation

