---
title: "Module 2"
subtitle: "Data science lifecycle & Quarto"
editor: source
params:
    week: 2
execute: 
  echo: false
  warning: false
bibliography: ../ds4owd-001.bib
---

Are you ready for some data visualisations? This week is all about exploring data with `ggplot2` R package. We will also learn about the data science lifecycle. 

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-02-ds4owd-001-learning-objectives.csv")) |> 
  dplyr::filter(week == params$week) |>
  dplyr::pull(learning_objectives)

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa display >}} Slides

- In preparation

## {{< fa book >}} Readings

1. Read [@wilson2017good]: "Good enough practices in scientific computing".
1. Read [R for Data Science - Section 1 - Introduction](https://r4ds.hadley.nz/intro) through **Section 1.3.3**
2. Read [R for Data Science - Whole game](https://r4ds.hadley.nz/whole-game)
3. Read [R for Data Science - Section 3 - Workflow basics](https://r4ds.hadley.nz/workflow-basics) 

## {{< fa code >}} Assignments

- In preparation


