---
title: "Module 10"
subtitle: "Questionnaires"
editor: source
params:
    module: 10
execute: 
  echo: false
  warning: false
---

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-01-rbtl-fs25-learning-objectives.csv")) |> 
  dplyr::filter(module == params$module) |>
  dplyr::pull(learning_objectives)

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa list >}} Class Overview

1.  During class we will be using the [files in this folder](https://drive.google.com/drive/folders/1BVi27abl-rDbxcK2aJyfz4keflBhW7Fv): there are [four different]{.highlight-yellow} .csv files for you to work with:
    a.  `01_binary.csv`
    b.  `02_likert.csv`
    c.  `03_multi-choice.csv`
    d.  `04_text.csv`
2.  There is also a corresponding [summary]{.highlight-yellow} file (e.g. `01_binary_summary`) with a tab for each group (groups from last week: wtp, compost, air, coops, mhm)
3.  Your group will
    a.  Download a data set
    b.  See what kind of data it is, and develop a corresponding research question (add to summary table)
    c.  Clean the data (use R) and note your process and any challenges you faced, and how you addressed them (add to summary table)
    d.  Analyse the data in a way that answers your research question (add result to summary table)
4.  We will discuss the pros and cons of each question type
5.  You will develop your own [questionnaire]{.highlight-yellow} to answer your research question

## {{< fa code >}} Assignments

Please complete the following assignment by Wednesday, 14th May 2024. 

-   [Assignment 1](../assignments/md-10/am-10-1-questionnaire.qmd): Develop a questionnaire using Google Forms
