---
title: "Module 10"
subtitle: "Questionnaires"
editor: source
params:
    module: 10
execute: 
  echo: false
  warning: false
---

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-01-rbtl-fs24-learning-objectives.csv")) |> 
  dplyr::filter(module == params$module) |>
  dplyr::pull(learning_objectives)

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa list >}} Class Overview

1.  During class we will be using the [files in this folder](https://drive.google.com/drive/folders/1BVi27abl-rDbxcK2aJyfz4keflBhW7Fv):  there are [four different]{.highlight-yellow} .csv files for you to work with:
    a.  `01_binary.csv`
    b.  `02_likert.csv`
    c.  `03_multi-choice.csv`
    d.  `04_text.csv`
2.  There is also a corresponding [summary]{.highlight-yellow} file (e.g. `01_binary_summary`) with a tab for each group (groups from last week:  wtp, compost, air, coops)
3.  Your group will
    a.  Download a data set
    b.  See what kind of data it is, and develop a corresponding research question (add to summary table)
    c.  Clean the data (use R, Excel, python, etc:  whatever you like) and note your process and any challenges you faced, and how you addressed them (add to summary table)
    d.  Analyse the data in a way that answers your research question (add result to summary table)
4.  We will discuss the pros and cons of each question type
5.  You will develop your own [questionnaire]{.highlight-yellow} to answer your research question

## {{< fa calendar-days >}} Class schedule

Here is the schedule for May 2:

|           |         |                    |                   |
|-----------|---------|--------------------|-------------------|
| **start** | **end** | **Topic**          | **Activity**      |
| 12:15     | 12:25   | Intro and Welcome  |                   |
| 12:25     | 12:45   | Research questions | Group discussions |
| 12:45     | 13:00   | Debugging          |                   |
| 13:00     | 13:15   | Break              |                   |
| 13:15     | 14:00   | 4 question types   | Group work        |
| 14:00     | 14:15   | Break              |                   |
| 14:15     | 15:00   | Consolidation      |                   |

## {{< fa code >}} Assignments

Please complete the following assignment by Wednesday, 15th May 2024. 

-   [Assignment 1](../assignments/md-10/am-10-1-questionnaire.qmd): Develop a questionnaire using Google Forms
