---
title: "Module 11"
subtitle: "{{< var md-11.title >}}"
editor: source
params:
    module: 11
execute: 
  echo: false
  warning: false
---

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-01-rbtl-fs24-learning-objectives.csv")) |> 
  dplyr::filter(module == params$module) |>
  dplyr::pull(learning_objectives)

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa display >}} Slides

-   There are no slides for this week

## {{< fa list >}} Class Overview

In class, everyone will:

1.  Complete everyone else's questionnaire and provide feedback in [this table](https://docs.google.com/spreadsheets/d/1LvaClheuJszxkIbLT0L-rRHEmgL_2h2o/edit#gid=133769975)
2.  Download the +/- 15 responses, and we will discuss any challenges related to the raw data

I will be available to discuss logistics, problems with questionnaires, etc. BUT if there is anything specific that anyone needs, do not hesitate to contact me beforehand (e.g. scales, buckets, etc.)

## {{< fa code >}} Assignments

-   In preparation
