---
title: "Capstone Project"
editor: source
params:
    week: 15
execute: 
  echo: false
  warning: false
editor_options: 
  chunk_output_type: console
---


```{r}
library(tidyverse)

grading <- read_csv(here::here("data/tbl-08-ds4owd-001-capstone-project-elements")) 
```

The Capstone Project report is the final assignment for this course and a completion is required to receive a course certificate about successful participation.


## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-02-ds4owd-001-learning-objectives.csv")) |> 
  dplyr::filter(week == params$week) |>
  dplyr::pull(learning_objectives)

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa code >}} GitHub repository

Establishing the GitHub repository with self-identified data was part of the homework assignment of module 5, 6, and 7. 

- [Module 5 - Assignment 1](../assignments/md-05/am-05-1-project-data.qmd): Identify data for your capstone project
- [Module 7 - Assignment 2](../assignments/md-07/am-07-2-project-metadata.qmd): Get going with your capstone project

It is important that these two assignments are completed before continuing with the write up of the report as outlined on this page. 

## {{< fa pen-clip >}} GitHub issue tracker

The GitHub issue tracker of each student's capstone project repository is used to communicate and ask questions about the Capstone Project report. Each course participant is assigned to one of the course instructors. 

## {{< fa calendar-check >}} Submission due date

The due date for submission of the report is **Tuesday, 13th February 2024**.

## {{< fa list-check >}} Required items

@tbl-required-items is a detailed list of items that need to be included for a complete submission of the capstone project report. Items are categorized into technical, data, and intellectual tasks. If any item is unclear, please reach out to the course instructors.

```{r}
#| label: tbl-required-items
#| tbl-cap: "List of items to be completed for the capstone project report."

grading %>% 
  select(no, category, items) %>% 
  knitr::kable()

```

