---
title: "Capstone Project"
editor: source
params:
    module: 11
execute: 
  echo: false
  warning: false
editor_options: 
  chunk_output_type: console
---


```{r}
library(tidyverse)

grading <- read_csv(here::here("data/tbl-10-rbtl-fs24-capstone-project-elements.csv")) 
```

The final capstone project provides students with an opportunity to apply their skills and techniques to real-world data sets. Each student will collect their own data for this project, either using a survey based tool (Google Forms) or an observational study (Google Sheets). A complete report receives 30 points.

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-01-rbtl-fs24-learning-objectives.csv")) |> 
  dplyr::filter(module == params$module) |>
  dplyr::pull(learning_objectives)

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa code >}} GitHub repository

The GitHub repository for this project was an assignment of Module 6. This repository will now be used to prepare the data and the final report:

- [Module 6 - Assignment 3](../assignments/md-06/am-06-3-project.qmd): Setup your capstone project repository

## {{< fa pen-clip >}} GitHub issue tracker

The GitHub issue tracker of each student's capstone project repository is used to communicate and ask questions about the Capstone Project report. It is up to the course participants to use this tool to ask questions and get feedback from the course instructors. The following GitHub usernames can be tagged: `@larnsce`, `@elizabeth-tilley`, `@bonschorno`.

## {{< fa calendar-check >}} Submission due date

The due date for submission of the report is **Tuesday, 06th June 2024**.

## {{< fa list-check >}} Required items

@tbl-required-items is a detailed list of items that need to be included for a complete submission of the capstone project report. Items are categorized into technical, data, and intellectual tasks. If any item is unclear, please reach out to the course instructors.

```{r}
#| label: tbl-required-items
#| tbl-cap: "List of items to be completed for the capstone project report."

grading |> 
  select(no, category, items, points) |> 
  knitr::kable()

```

## {{< fa Upload >}} Publish report to GitHub Pages

This step is not a part of the required items that final report should be published on GitHub Pages. The report should be a single HTML file that includes all the required items. The report should be named `index.html` and should be placed in the root directory of the repository. The report should be accessible via the URL: `https://<username>.github.io/<repository-name>/index.html`.
